Har en persons høyde innvirkning på lønnen?

### 2020-11-01 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd

---
title: "Har en persons høyde innvirkning på lønnen?"
subtitle: "Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20"
author: 
  - Katrine Hope
  - Karl-Gunnar Severinsen
classoption: twoside
fontsize: 12pt
linestretch: 1.5
output:
  pdf_document:
    df_print: paged
    toc: true
    toc_depth: 3
    fig_height: 4
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

```{r age_facet-ag, echo=F}
#Mitt forslag
heights %>%
  group_by(sex) %>% 
  mutate(
    height_cmInt = cut_interval(height_cm, breaks = c(132, 160, 188, 216), labels = c("lav", "middels", "høy"), right = FALSE)
  ) %>% 
  ungroup() %>% 
  ggplot(mapping = aes(x = height_cm, 
                           y = inntekt
                       )
         ) +
    facet_wrap(sex ~ height_cmInt) +
  geom_point(mapping = aes(colour = cut_number(age, 
                                     n = 3)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

>>>>

---
title: "Har en persons høyde innvirkning på lønnen?"
subtitle: "Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20"
author: 
  - Katrine Hope
  - Karl-Gunnar Severinsen
classoption: twoside
fontsize: 12pt
linestretch: 1.5
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float: true
  pdf_document:
    df_print: paged
    toc: true
    toc_depth: 3
    fig_height: 4
---

@@
